\LARGE \bf Detection and Mitigation of Corrupted Information in Distributed Model Predictive Control Based on Resource Allocation

### 2021-08-26 article/article.tex
add IEEE copyright

\input{preamble}
% \usepackage[showframe]{geometry}
\usepackage{geometry}
\usepackage{stfloats}
\geometry{
  textwidth=\columnwidth,
  top=19.1mm,
  bottom=36.7mm,
  left=19.1mm,
  right=13.1mm,
}

@@

\draft%
% \final%

\makeglossaries
\begin{document}
\maketitle
% \IEEEpeerreviewmaketitle% This command is only
\thispagestyle{empty}
\pagestyle{empty}

@@

\section{PRELIMINARIES AND PROBLEM STATEMENT}\label{sec:PS}
\emph{Notation:} In this paper, $\|\cdot\|$ and $\|\cdot\|_{F}$ represent the $\ell_{2}$ and Frobenius norms. $\|\vec{v}\|_{Y}$ is the weighted norm, $\|Y^{1\over 2}\vec{v}\|$.
$P_{\mathsf{T}}(\cdot)$ is the Euclidean projection onto set $\mathsf{T}$.
$\otimes$ represents the Kronecker product. $\1_{m,n}$ is a ${m\times n}$ matrix filled with $1$.
$I_{c}$ is a ${c\times c}$ identity matrix.
$\pi_{v}$ denotes the number of elements in $v$.
A vector $\vec{v}_{i}$, correspond to the $i$-th agent, and these vectors can be stacked in a vector $\vec{v}$.

@@

\end{matrix}
\label{eq:dmpcModLOP}
\end{equation*}
with symmetric weight matrices ${Q_{i}\geq0}$, ${R_{i}>0}$. $\vec{v}_{i}(k)$ represents a control objective. It can either be ${\vec{v}_{i}(k)=\vec{w}_{i}(k)-\vec{x}_{i}(k)}$ for reference tracking, where $\vec{w}_{i}(k)$ is a state reference, or ${\vec{v}_{i}(k)=\vec{x}_{i}(k)}$ for disturbance rejection.

>>>>

\input{preamble}
% \usepackage[showframe]{geometry}
\usepackage{geometry}
\usepackage{stfloats}
\geometry{
  top=19.1mm,
  bottom=36.7mm,
  left=19.1mm,
  right=13.1mm,
}

@@

% \draft%
\final%
\newcommand{\id}{}
\newcommand{\price}{31.00}
\pubid{\begin{minipage}{\textwidth}\ \\[50pt]\centering
  \copyright 2021 IEEE. Personal use is permitted, but republication/redistribution requires IEEE permission.\\
See https://www.ieee.org/publications/rights/index.html for more information.
\end{minipage}}
% \makeglossaries
\markboth{Oi}{test}
\begin{document}
\maketitle
% \IEEEpeerreviewmaketitle% This command is only
% \thispagestyle{empty}
% \pagestyle{empty}

@@

\section{PRELIMINARIES AND PROBLEM STATEMENT}\label{sec:PS}
\emph{Notation:} In this paper, $\|\cdot\|$ and $\|\cdot\|_{F}$ represent the $\ell_{2}$ and Frobenius norms. $\|\vec{v}\|_{Y}$ is the weighted norm, $\|Y^{\frac{1}{2}}\vec{v}\|$.
$P_{\mathsf{T}}(\cdot)$ is the Euclidean projection onto set $\mathsf{T}$.
$\otimes$ represents the Kronecker product. $\1_{m,n}$ is a ${m\times n}$ matrix filled with $1$.
$I_{c}$ is a ${c\times c}$ identity matrix.
$\pi_{v}$ denotes the number of elements in $v$.
A vector $\vec{v}_{i}$, correspond to the $i$-th agent, and these vectors can be stacked in a vector $\vec{v}$.

@@

\end{matrix}
% \label{eq:dmpcModLOP}
\end{equation*}
with symmetric weight matrices ${Q_{i}\geq0}$, ${R_{i}>0}$. $\vec{v}_{i}(k)$ represents a control objective. It can either be ${\vec{v}_{i}(k)=\vec{w}_{i}(k)-\vec{x}_{i}(k)}$ for reference tracking, where $\vec{w}_{i}(k)$ is a state reference, or ${\vec{v}_{i}(k)=\vec{x}_{i}(k)}$ for disturbance rejection.
